\clearpage
\makeatletter
\efloat@restorefloats
\makeatother


\begin{appendix}
\section{}
\hypertarget{experiment-1}{%
\subsection{Experiment 1}\label{experiment-1}}

\hypertarget{video-a-6-11.9-months-pick-it-up}{%
\subsubsection{Video A (6-11.9 months) ``Pick it
up''}\label{video-a-6-11.9-months-pick-it-up}}

Parents are told to encourage their child to pick up and drop individual
objects. They are also encouraged to place toys on a small cloth and
show the child that they can drag the cloth towards them to reach the
toys.

Props: cloth, plastic horse, plastic sheep, plastic elephant, toy car

\hypertarget{video-b-6-11.9-months-animal-sounds}{%
\subsubsection{Video B (6-11.9 months) ``Animal
sounds''}\label{video-b-6-11.9-months-animal-sounds}}

Parents are told to call different animals and imitate different sounds
the animals make. They are also encourgaed to observe which animal the
child prefers.

Props: plastic sheep, plastic horse, plastic frog, plastic cow, bowls

\hypertarget{video-c-12-17.9-months-give-me-the-toy}{%
\subsubsection{Video C (12-17.9 months) ``Give me the
toy''}\label{video-c-12-17.9-months-give-me-the-toy}}

Parents are told to ask their child to hand over individual toys. They
are also encouraged to praise the child after they give them the toys,
and repeat the process until the child could follow the verbal
instructions.

Props: toy boat, plastic frog, plastic elephant, toy bus

\hypertarget{video-d-12-17.9-months-classifying-my-toys}{%
\subsubsection{Video D (12-17.9 months) ``Classifying my
toys''}\label{video-d-12-17.9-months-classifying-my-toys}}

Parents are told to place toys of different sizes (big or small) in two
hoops. They are also encouraged to ask their child to distinguish
between two objects and identify which one is larger.

Props: two yellow and green rings, big car, small car, big horse, small
horse

\hypertarget{video-e-18-23.9-months-my-toys}{%
\subsubsection{Video E (18-23.9 months) ``My
toys''}\label{video-e-18-23.9-months-my-toys}}

Parents are told to show the child toys of the same shape but different
sizes, to place one of the objects in a basket and to ask the child to
take out the object. They are also encouraged to ask their child if the
object is bigger or smaller compared to its pair.

Props: two buckets, big car, small car, big horse, small horse

\hypertarget{video-f-18-23.9-months-the-orchestra}{%
\subsubsection{Video F (18-23.9 months) ``The
Orchestra''}\label{video-f-18-23.9-months-the-orchestra}}

Parents are told to give their child a musical instrument to play. They
are also encouraged to play a song and see if the child follows the
rhythm.

Props: maracas, drum, tambourine, clapper

\hypertarget{experiment-2}{%
\subsection{Experiment 2}\label{experiment-2}}

\hypertarget{video-a-12-17.9-months-give-me-the-toy}{%
\subsubsection{Video A (12-17.9 months) ``Give me the
toy''}\label{video-a-12-17.9-months-give-me-the-toy}}

Parents are told to ask their child to hand over individual toys. They
are also encouraged to praise the child after they give them the toys,
and repeat the process until the child could follow the verbal
instructions.

Props: plastic pig, plastic horse, plastic dog, plastic cat, plastic cow

\hypertarget{video-b-12-17.9-months-classifying-my-toys}{%
\subsubsection{Video B (12-17.9 months) ``Classifying my
toys''}\label{video-b-12-17.9-months-classifying-my-toys}}

Parents are told to place toys of different sizes (big or small) in two
hoops. They are also encouraged to ask their child to distinguish
between two objects and identify which one is larger.

Props: two yellow and green rings, big car, small car, big horse, small
horse

\hypertarget{video-c-12-17.9-months-geometric-shapes-jigzsaw-puzzle}{%
\subsubsection{Video C (12-17.9 months) ``Geometric shapes jigzsaw
puzzle''}\label{video-c-12-17.9-months-geometric-shapes-jigzsaw-puzzle}}

Parents are told to encourage their child to name different shapes on a
jigzsaw puzzle. Then they are told to undo the puzzle and invite the
child to complete the puzzle.

Props: A jigzsaw puzzle of geometric shapes

\hypertarget{video-d-18-23.9-months-my-toys}{%
\subsubsection{Video D (18-23.9 months) ``My
toys''}\label{video-d-18-23.9-months-my-toys}}

Parents are told to show the child toys of the same shape but different
sizes, to place one of the objects in a basket and to ask the child to
take out the object. They are also encouraged to ask their child if the
object is bigger or smaller compared to its pair.

Props: two buckets, big car, small car, big horse, small horse

\hypertarget{video-e-18-23.9-months-the-orchestra}{%
\subsubsection{Video E (18-23.9 months) ``The
Orchestra''}\label{video-e-18-23.9-months-the-orchestra}}

Parents are told to give their child a musical instrument to play. They
are also encouraged to play a song and see if the child follows the
rhythm.

Props: maracas, drum, tambourine, clapper

\hypertarget{video-f-18-23.9-months-my-yellow-toys}{%
\subsubsection{Video F (18-23.9 months) ``My Yellow
Toys''}\label{video-f-18-23.9-months-my-yellow-toys}}

Parents are told to show their child yellow toys and to ask, ``What
color are they?'' They are also told to give the child toys of different
colors, to ask them to only play with the yellow ones, and to praise the
child after they do so.

Props: blue car, yellow car, yellow block, red block, blue block, green
block
\end{appendix}
